Owl Occupancy in Three of El Salvador's Protected Areas from 2003 through 2013

### 2021-02-27 manuscript_working/ms_working_RMD.tex
incorporated MRE/AAA edits

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={working owls methods},
            pdfauthor={Althea Archer},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\title{working owls methods}
\author{Althea Archer}
\date{11/3/2020}

@@

\section{Methods}\label{methods}

\subsection{Occupancy Model}\label{occupancy-model}

Let

\[
\begin{aligned}
t  &=  \text{the years of surveys (here }t = 1,2,\ldots,11)\\
h  &=  \text{the individual routes (here }h = 1,2,\ldots,6)\\
i  &=  \text{the individual surveys conducted in each year and route (here }i = 1,2,3)\\
j  &=  \text{the individual stations along each route (here }j = 1,2,\ldots,10)\\
k  &=  \text{the broadcast species (here }k = 1,2,\ldots,10)\\
z_{t,h,i} &= \text{a random variable equal to 1 when a survey was occupied and 0 otherwise}\\
y_{t,h,i,j,k} &= \text{a random variable equal to 1 when an owl was detected and 0 otherwise}
\end{aligned}
\]

We assumed that survey occupancy (\(z_{t,h,i}\)) was the outcome of
Bernoulli trials with probability \(\psi\), which we allowed to vary by
year and route:

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Owl Occupancy in Three of El Salvador's Protected Areas from 2003 through 2013},
  pdfauthor={Jane West and Althea Archer},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\title{Owl Occupancy in Three of El Salvador's Protected Areas from 2003
through 2013}
\author{Jane West and Althea Archer}
\date{2/27/2021}

@@

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

As apex predators, owls are an important bioindicator of ecosystem
health, though much of our understanding comes from temperate systems
(White et al. 2013, Wan et al. 2018, Buechley et al. 2019). In the
tropics, particularly in rain and cloud forests, owl studies are more
difficult than in temperate regions, regardless of potentially denser
populations (König and Weick 1999), and neotropical owls are less
well-studied than their temperate counterparts {[}Buechley:2019{]}.
Further, the neotropics were identified by Buechley et al. (2019) as a
priority area for owl research, based on an extensive literature review
that identified a relative lack of research attention and a high
conservation risk for neotropical owls. As a result, we have limited
understanding of neotropical owls' distribution, ecological
requirements, population dynamics, and reproductive behavior (Clark et
al. 1978, Enríquez et al. 2006, Pérez-Léon et al. 2017, Rangel-Salazar
and Enríquez 2017). This lack of information poses a challenge to
proactive conservation, even as neotropical habitat experiences
tremendous anthropogenic pressure and rapid, unpredictable responses to
climate change (Corlett 2012). In general, while our knowledge about the
status and trends of neotropical owl populations is limited, we do know
that owl abundance and distribution is decreasing in several regions
where species have been added to endangered species lists or have become
locally extirpated (Enríquez et al. 2006).

Like many owl species, neotropical owls are difficult to accurately
census due to their cryptic nature and nocturnal habits. Vocalizations
of crepuscular and cryptic animals such as owls are commonly leveraged
in survey methodology (König and Weick 1999). Owl vocalizations can be
diagnostic and are often considered more practically attainable than
visual identification. Owls vocalize to communicate with the same
species, to threaten or provoke other species, and to delimit territory
(Johnsgard 1988).

Vocalization surveys for nocturnal birds of prey fall generally into two
categories. Spontaneous or ``passive'' surveys involve listening for
animal calls with no prior stimulus, whereas provocation or
``broadcast'' surveys are conducted by listening after a period of
playing a recording of animal vocalizations (e.g., Baumgardt et al.
2019). The inclusion of broadcast calls in auditory surveys can increase
the detection probability of owls, although intra- and inter-species
interactions can play a role whether owls are more likely or less likely
to call in response to a vocalization simulus (Enrı́quez and Salazar
1997, Borges et al. 2004, Flesch and Steidl 2007, Baumgardt et al.
2019).

The objective of our study was to collect occupancy data on El Salvador
owls through time to determine both the population dynamics of
individual owl species and the overall community composition of owls in
three targeted protected areas, El Imposible National Park, Montecristo
National Park, and Nancuchiname Forest. El Salvador is located in the
heart of the Mesoamerican Biodiversity Hotspot (Myers and Mittermeier
2000), and we selected three survey areas in protected landscapes to
represent the breadth of ecosystem diversity across the country. We set
up two routes in each protected area and conducted nighttime foot
surveys using passive listening and broadcast calls during the breeding
season for three weeks during each year from 2003 through 2013.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{study-area}{%
\subsection{Study area}\label{study-area}}

El Salvador is located on the western side of the Central American
isthmus and is the smallest and most densely populated Central American
country (Central Intelligence Agency 2020). It is bordered by the
Pacific Ocean, Guatemala and Honduras (Fig. 1XXX). Overall, 13.6\% of El
Salvador's 20,720 km\(^2\) of land is forest and 82\% is used for
agricultural purposes (Central Intelligence Agency 2020). We conducted
surveys in three protected natural areas located at different elevations
(high, mid and low elevations) and in different types of forest
vegetation (alluvial, deciduous, semi-deciduous, pine-oak and cloud
forest) that represent a portion of the country's diverse ecosystems
(Fig. 1xxx, Table 1XXX).

El Imposible National Park (NP) was located 119 km southwest of San
Salvador (Fig. 1XXX, Table 1XXX). Its elevation ranged from 250 to 1425
m above sea level (a.s.l.). It was the largest NP in the country,
covering 3792 ha, and its elevation ranged from 250 to 1425 m a.s.l..
The topography of El Imposible was extremely steep and broken, with many
cliffs (Álvarez and Komar 2003). The area contained deciduous and
semi-deciduous forest, secondary growth vegetation on the edges, and
former pasture areas that were reforested with native species in 1997.
We established one survey route (EI-1) in the western portion of El
Imposible in an area of reforestation and at a low elevation and a
second survey route (EI-2) in an area of semi-deciduous forest.

Montecristo NP (1973 ha) was located 125 km northwest of San Salvador
(Fig. 1XXX; Table 1XXX). Its altitude ranged from 730 to 2418 m a.s.l.
(Ministerio de Medio Ambiente y Recursos Naturales 2010). High
elevations of Montecristo contained cloud forest, middle elevations
contained pine/oak forest (with some pine and cypress plantations) and
the lower elevations contained a semi-deciduous tropical forest
(Ministerio de Medio Ambiente y Recursos Naturales 2015a). This NP was
part of the Montecristo Tri-national Protected Area which included
extensive adjoining natural areas in Guatemala and Honduras (Komar
2010). Within Montecristo, we established one survey route (M-1) in a
cloud forest and another (M-2) at a moderate elevation in a pine/oak
forest.

Nancuchiname Forest (797 ha) is a Protected Natural Area located 95 km
southeast of San Salvador in the coastal alluvial plain along the Lempa
River (Fig. 1XXX). Its elevation ranged from sea level to 12 m a.s.l.
The area contained deciduous and semi-deciduous forest, second growth
vegetation, native species reforestation and a dike surrounded by
secondary growth. In Nancuchiname Forest, we established one survey
route (N-1) in alluvial forest along the dike and the other route (N-2)
in a semi-deciduous alluvial forest.

\emph{Table 1XX. Route locations and habitats. Owl surveys were
conducted from 2003 to 2013 in three different protected areas within El
Salvador: El Imposible National Park (EI-1 and EI-2), Montecristo
National Park (M-1 and M-2) and Nancuchiname Forest (N-1 and N-2). }

\begin{longtable}[]{@{}ccccc@{}}
\toprule
\begin{minipage}[b]{0.08\columnwidth}\centering
Route\strut
\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\centering
Latitude\strut
\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\centering
Longitude\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Elevation\strut
\end{minipage} & \begin{minipage}[b]{0.35\columnwidth}\centering
Habitat\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.08\columnwidth}\centering
EI-1\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
13xx 50.75'\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
89xx 59.74'\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
609\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\centering
Reforested deciduous forest\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.08\columnwidth}\centering
EI-2\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
13xx 51.38'\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
89xx 58.24'\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
958\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\centering
Semi-deciduous forest\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.08\columnwidth}\centering
M-1\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
14xx 24.88'\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
89xx 21.63'\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
2111\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\centering
Cloud forest\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.08\columnwidth}\centering
M-2\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
14xx 23.19'\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
89xx 22.33'\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
1755\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\centering
Pine/oak forest\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.08\columnwidth}\centering
N-1\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
13xx 19.95'\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
88xx 43.63'\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
3\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\centering
Alluvial forest with secondary growth\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.08\columnwidth}\centering
N-2\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
13xx 22.03'\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
88xx 43.30'\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
2\strut
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\centering
Alluvial forest\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{survey-methods}{%
\subsection{Survey methods}\label{survey-methods}}

We conducted acoustic surveys on foot following the Guidelines for
Nocturnaal Owl Monitoring (Takats et al. 2001), a similar protocol
developed for Costa Rica (Enrı́quez and Rangel-Salazar 2001), and other
raptor research guidelines (Fuller and Mosher 1987). This study's survey
protocol was an extension of previous research completed in the western
half of El Imposible NP (West 1988). We created six 2-km long survey
routes (transects) that each included 10 permanent survey stations set
at 200 m intervals. Two routes were established in each protected area
(Table 1xxx).

Surveys began at local twilight and took approximately five hours to
complete. At each station, we measured and recorded environmental
conditions (Brunton Sherpa, Brunton Incorporated) including temperature,
precipitation, cloud cover, fog cover, wind speed, barometric pressure,
moon phase, and noise level. The acoustic survey then began with passive
listening for two minutes, followed by a three-minute broadcast call,
and ending with seven minutes of silent listening. We recorded local owl
vocalizations and used them for broadcast calls whenever possible. If an
owl vocalized during broadcast playback, we stopped the broadcast and
recorded the owl's vocalization. When we detected an owl, we noted its
location and bearing relative to the station, and we tracked when the
same owl was identified at consecutive stations.

The broadcast calls varied between routes, but were consistent at each
route and station across years. Specifically, we broadcast the
vocalizations of Pacific Screech-Owls (\emph{Megascops cooperi}),
Mottled Owls (\emph{Ciccaba virgata}), Crested Owls (\emph{Lophostrix
cristata}), Black-and-white Owls (\emph{C. nigrolineata}), Spectacled
Owls (\emph{Pulsatrix perspicillata}), Pacific Screech-Owls, Mottled
Owls, Crested Owls, Black-and-white Owls, and Spectacled Owls at
stations 1 through 10, respectively, in all routes in El Imposible NP
(EI-1 and EI-2) and Nancuchiname Forest (N-1 and N-2). We broadcast the
vocalizations of Whiskered Owls (\emph{M. trichopsis}), Mottled Owls,
Fulvous Owls (\emph{Strix fulvescens}), Stygian Owls (\emph{Asio
stygius}), Great Horned Owls (\emph{Bubo virginianus}), Whiskered Owls,
Mottled Owls, Fulvous Owls, Stygian Owls, and Great Horned Owls at
stations 1 through 10, respectively, in both routes of Montecristo NP
(M-1 and M-2).

Surveys were repeated at each route up to three times a year from 2003
through 2013, depending on site access and weather. We did not conduct
any surveys in 2006. We georeferenced the owl detections for each survey
and route to eliminate double counting of individual owl observations.

\emph{Table 2XX. Species detection records by route. Owl surveys were
conducted from 2003 to 2013 in three different protected areas within El
Salvador, although specific survey years varied by route.}

\begin{longtable}[]{@{}ccccccc@{}}
\toprule
\begin{minipage}[b]{0.31\columnwidth}\centering
Name\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
EI-1\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
EI-2\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\centering
M-1\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\centering
M-2\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\centering
N-1\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\centering
N-2\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.31\columnwidth}\centering
Barn Owl\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
8\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
2\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
(Tyto alba)\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
Whiskered Screech-Owl\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
2\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
(Megascops trichopsis)\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
Pacific Screech-Owl\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
11\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
1\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
6\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
9\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
(Megascops cooperi)\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
Crested Owl\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
(Lophostrix cristata)\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
Spectacled Owl**\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
1\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
1\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
1\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
59\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
75\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
(Pulsatrix perspicillata)\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
Great Horned Owl\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
3\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
(Bubo virginianus)\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
Ferruginous Pygmy-Owl\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
4\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
82\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
98\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
(Glaucidium brasilianum)\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
Burrowing Owl\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
(Athene cunicularia)\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
Mottled Owl\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
214\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
117\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
1\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
22\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
62\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
114\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
(Ciccaba virgata)\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
Black-and-white Owl**\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
(Ciccaba nigrolineata)\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
Fulvous Owl*\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
17\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
(Strix fulvescens)\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
c.f. Stygian Owl\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0\strut
